\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Arian Alai}} \\
    Lincoln, Nebraska, United States \\
    +1(402) 689-5468 \\

\end{center}

% Professional Summary
\section*{Professional Summary}
Data science professional with 2 years of business intelligence experience and 2 years of mathematics \& statistics tutoring experience. Passionate about leveraging data-driven insights to drive strategic decision-making and foster organizational growth. Proficient in Python, R, Excel, SQL, Tableau, and Grafana.

% Professional Experience
\section*{Professional Experience}

\textbf{Graduate Teaching Assistant} \\
University of Nebraska-Lincoln \hfill August 2024 - Present
\begin{itemize}[noitemsep, topsep=0pt]
    \item Lead introductory statistics courses and lab sessions.
    \item Create supportive learning environments and deliver lessons.
    \item Provide timely, constructive feedback on assignments and exams.
    \item Foster statistical literacy and analytical thinking among students.
\end{itemize} 
\textbf{Business Intelligence Analyst} \\
Sandhills Global, Lincoln, Nebraska \hfill August 2023 - August 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Analyzed data from Sandhills products and services to enhance customer satisfaction.
    \item Streamlined internal processes through automation using SQL, R, and Python.
    \item Developed and maintained interactive dashboards using Tableau and Grafana.
    \item Ensured data accuracy and quality through rigorous quality assurance processes.
\end{itemize}
\textbf{Business Intelligence Intern} \\
Sandhills Global, Lincoln, Nebraska \hfill September 2022 - August 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Reviewed and analyzed data from Sandhills products and services.
    \item Collaborated with Data Science team to apply insights to market challenges.
    \item Created internal reporting features to streamline information processing.
    \item Utilized Microsoft Excel, Azure, Jenkins, SQL, Tableau, R, and Python.
\end{itemize}
\textbf{Business Analyst Intern} \\
Sandhills Global, Lincoln, Nebraska \hfill August 2022 - September 2022
\begin{itemize}[noitemsep, topsep=0pt]
    \item Designed and developed processes for internal and external task order systems.
    \item Collaborated with Business Analysts and Software Developers on logical and analytical-based projects.
\end{itemize}
\textbf{Investor Services Intern} \\
Charles Schwab, Omaha, Nebraska \hfill June 2022 - August 2022
\begin{itemize}[noitemsep, topsep=0pt]
    \item Assisted clients with TD Ameritrade accounts.
    \item Collaborated with interns on business project.
    \item Prepared for Securities Industry Essentials (SIE) Exam to deepen finance knowledge.
\end{itemize}
\textbf{Peer Tutor} \\
Doane University, Crete, Nebraska \hfill August 2021 - May 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Provided tutoring in mathematics, data analytics, and financial accounting courses.
    \item Customized teaching styles for 14 individual students and 3 test-prep classes.
    \item Assisted tutoring coordinator in improving Doane's tutoring system.
\end{itemize}
% Professional Projects
\section*{Professional Projects}

\textbf{Sandhills Global (2022-Present)}

\subsection*{AI and Machine Learning Systems}

\textbf{AI Content Filtering Enhancement} \hfill Jul 2024 - Aug 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Implemented granular content filtering based on publication and location.
    \item Developed scripts for tag data collection and integration with Redis and Qdrant databases.
    \item Enhanced AI system responsiveness and search accuracy.
\end{itemize}
\textbf{vLLM System Monitoring} \hfill May 2024 - Jun 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Designed Grafana dashboard for monitoring Virtual Large Language Model performance.
    \item Configured Prometheus to track key metrics including memory usage, CPU utilization, and request latency.
    \item Enabled real-time system performance monitoring and proactive resource management.
\end{itemize}
\textbf{AI System API Integration} \hfill Mar 2024 - Apr 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Modernized chatbot infrastructure by replacing external API calls with internal integrations.
    \item Implemented three new endpoints for improved data access.
    \item Streamlined system architecture for enhanced maintainability.
\end{itemize}

\subsection*{Data Analytics and Visualization}

\textbf{Advanced Tableau Extensions Development} \hfill May 2023 - Aug 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Integrated R and Python capabilities with Tableau using Rserve and TabPy.
    \item Implemented advanced analytics including SARIMAX forecasting, DBSCAN clustering, and PCA.
    \item Enhanced data visualization capabilities beyond native Tableau features.
\end{itemize}
\textbf{Market Data Integration} \hfill Feb 2024 - Mar 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Enhanced monthly market reports with retail sales and brand-specific pricing data.
    \item Created new dashboards for metric tracking and trend analysis.
    \item Improved stakeholder decision-making through comprehensive market insights.
\end{itemize}
\textbf{Listings Analysis Dashboard} \hfill Aug 2023 - Oct 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Expanded Tableau report with new dashboard for tracking net listings.
    \item Implemented metrics for Added/Dropped Listings and Top Net Listings by category.
    \item Provided sales team with actionable inventory change insights.
\end{itemize}
\textbf{Data Pipeline Automation} \hfill Jun 2023 - Dec 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Automated serial number data import process using R.
    \item Reduced processing time from several days to 15 minutes.
    \item Developed SQL queries and data condensation algorithms.
\end{itemize}

\subsection*{Infrastructure and Monitoring}

\textbf{Health Check Dashboard Implementation} \hfill Jan 2024
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed Grafana dashboard for ML stack health monitoring.
    \item Implemented Prometheus metrics for service status tracking.
    \item Enabled rapid issue identification and system health assessment.
\end{itemize}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Established Spark monitoring on Kubernetes cluster.
    \item Created Grafana dashboard for resource and job metrics.
    \item Improved visibility into Spark job performance and resource utilization.
\end{itemize}

\subsection*{Data Collection and Analysis}

\textbf{Production Data Analytics} \hfill May 2023 - Sep 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Developed web scraper for production data collection.
    \item Implemented data validation and reporting systems.
    \item Streamlined data integration processes.
\end{itemize}
\textbf{Tableau System Audit} \hfill Apr 2023 - Sep 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Conducted comprehensive audit of internal Tableau content.
    \item Created tracking system for workbook usage and user engagement.
    \item Developed dashboard for content management and archival decisions.
\end{itemize}
\textbf{Stored Procedure Implementation} \hfill Nov 2022 - May 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Created logging system using R and SQL.
    \item Created Tableau dashboard to visualize category data.
    \item Authored related documentation for BI analysts and data scientists.
\end{itemize}
\textbf{Market Data Automation} \hfill Oct 2022 - Jan 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Automated website data scraping and reporting processes.
    \item Developed Tableau dashboard for marketing team analysis.
    \item Identified potential customer leads through trend analysis.
\end{itemize}
\textbf{Hurricane Ian Impact Analysis} \hfill Oct 2022 - Feb 2023
\begin{itemize}[noitemsep, topsep=0pt]
    \item Analyzed equipment inventory in hurricane-affected areas using USGS data.
    \item Created SQL queries for location-based analysis.
    \item Developed Tableau visualization for tracking assets affected by hurricane.
\end{itemize}

\subsection*{}

\textbf{Charles Schwab (2022)}

\subsection*{Business Analysis}

\textbf{COVID-19 Client Support Enhancement} \hfill Jul 2022
\begin{itemize}[noitemsep, topsep=0pt]
    \item Analyzed client needs during pandemic with intern team.
    \item Conducted research on financial service delivery improvements.
    \item Developed recommendations for enhanced client engagement.
\end{itemize}

\subsection*{}


\textbf{Doane University (2022)}

\subsection*{Academic Research}

\textbf{Student Debt Analysis Project} \hfill Sep 2022 - Dec 2022
\begin{itemize}[noitemsep, topsep=0pt]
    \item Conducted statistical analysis of Nebraska student debt using Department of Education data.
    \item Created linear models to analyze loan relationships.
    \item Developed predictive models for loan repayment rates.
\end{itemize}

% Education
\section*{Education}
\textbf{Master's Degree} \\
University of Nebraska-Lincoln \\
In Progress\\\\
\textbf{Bachelor's Degree} \\
Doane University \\
Graduated May 2023

% Publications
\section*{Publications}

Colclasure, Blake, Alai, Arian, Quinn, Kristina, Granberry, Tyler, Doyle, Erin, \& Durham Brooks, Tessa. (2024). \textit{Voices from Graduate School and the Workforce: Identified Student Outcomes from Completing a Multi-Semester Undergraduate Research Experience Capstone}. \textit{Education Sciences}, 14, 598. \href{https://doi.org/10.3390/educsci14060598}{10.3390/educsci14060598}.


% Skills
\section*{Skills}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Data Analysis and Visualization
    \item Statistical Analysis and Machine Learning
    \item Python, R, SQL, Tableau, Grafana
    \item Business Intelligence
    \item Problem Solving and Troubleshooting
    \item Communication and Teamwork
    \item Teaching and Mentoring
\end{itemize}

% Awards
\section*{Awards}
\begin{itemize}[noitemsep, topsep=0pt]
    \item Tutor of the Year, 2023 - Doane University
\end{itemize}

\end{document}
